---
title: "Final Project Report - Developing Data Products Course"
author: "Tongesai Kapondo"
date: "26 June 2016"
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

 

```{r set-options, echo=FALSE, cache=FALSE}
## # How to adjust the output width of RStudio Markdown output (to HTML)
options(width = 200) # SOME-REALLY-BIG-VALUE
```

## Agenda

1.	Background/Motivation
2.	Code for plots
3.	Guidelines to reproduce locally
4.	For more information


## Background/Motivation

The body mass index (BMI) is a value derived from the mass (weight) and height of an individual. The BMI is defined as the body mass divided by the square of the body height, and is universally expressed in units of $\frac{kg}{m^2}$, resulting from mass in kilograms and height in metres.

## Formula for Calculation of the Body Mass Index (BMI)

This app helps to calculate a simple body mass index (BMI) using a simple formula :

$$ \LARGE BMI = \frac {mass_{kg}}{height_m^2} $$



This app calculates the BMI of individuals by entering the mass [kg] and the height [m].

The apps and documentation are found here: The Slidify presentation is found as index.html

web app: [Web App](https://kapondot.shinyapps.io/DevelopingDataProjects/)

GitHub Repo: [GitHub Repo](https://github.com/Kapondo/Dataproducts)

## Guidelines to reproduce locally

To run locally this App on your computer you do NOT need to fork this repo. Please follow these instructions:
Install the necessary packages to run RStudio's Shiny locally. 

## Conclusion

Test all documentation please for reproducibility
