---
title       : Developing Data Products Project
subtitle    : Calculation of the Body Mass Index (BMI)
author      : Tongesai Kapondo 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax, bootstrap] # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---


## INTRODUCTION
This presentation is part of the Course Project for the Coursera Developing Data Products class. The peer assessed assignment has two parts. First, we need to create a Shiny application and deploy it on Rstudio's servers. Second, we should use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about the application. This presentation adresses the second part of the course project.
The app developed for the first part of the assignment is avalilable [here](https://kapondot.shinyapps.io/DevelopingDataProjects/):

Source code for ui.R and server.R files are available on the [Kapondo GitHub repo](https://github.com/Kapondo/Dataproducts):


--- .class #id 

## Calculation of the Body Mass Index (BMI)

This app helps to calculate a simple body mass index (BMI) using a simple formula :$\LARGE BMI = \frac {mass_{kg}}{height_m^2}$

The app is only applicable where ther units on mass are in kg and the units of height are in meters.


## General Table of BMI 

Category |	BMI |($\frac{kg}{m^2}$) 
---------|-------|-----------------
          | from | to
Very severely underweight |  	|15.0
Severely underweight    |15	    |16
Underweight	|16	| 18.5
Normal (healthy weight) |	18.5 |	25
Overweight	| 25 |	30
Obese Class I (Moderately obese) |	30 |	35


--- .class #id

## Function for calculating BMI

```{r}
BMI <- function(m, h){
    m/h^2
}
paste("If your mass is", m = 90, "and your height is:", h=1.75)

paste("Your body mass BMI is: ", BMI(90, 1.75))
```

--- .class #id

## Importing and Plotting Data from SADC countries
```{r, set-options, echo=FALSE, cache=FALSE}
options(width = 400, height = 400) 
library(readr)
SADCBMI <- read_csv("D:/R/SLIDIFY/MyDeck/SADCBMI.csv"); attach(SADCBMI)
countrycolorscores <- c(22, 25, 9.5, 17,8.5,7.1,11.5,
                        8.5,20,9.2,35,21,7.5,9.8,10.5)
testcolors <- ifelse(countrycolorscores>=30, "red", "#03b3f3")
xlab <- SADCBMI[, 1]
mp <-barplot(height = BMI_percent, names.arg = Country, axisnames = FALSE,  col = testcolors)
text(mp, par("usr")[3], labels = xlab, srt = 45, adj = c(1.1,1.1), xpd = TRUE, cex=1, ylab = "BMI>=30 (%)")
axis(2)
```
**Conclusion:** From Analysis of different Countries in the SADC region, **South Africa** has the highest percentage of people with a **BMI>=30** of **35%** as indicated in red colour
